Analysis of gene regulatory properties underlying pleiotropy between complex traits

### 2022-11-12 presentation_gold2022_paris/presentation_gold2022_paris.tex
ENH

\begin{itemize}
\item Disease clusters are coherent $\rightarrow$ Validates approche and data
\item Definition of disease classes
\end{itemize}

@@

More egenes per variant-etissue pair.

@@

\begin{itemize}
\item This could explain why pleiotropic variants active in more etissues and associated to more egenes
\end{itemize}

@@

Outcomes interesting for the GOLD population genotypes
%
\begin{itemize}
\item A large set of causal GWAS variants annotated with target genes and tissues
\item A list of pleiotropic variants and regions
\end{itemize}
%
\vfill
%
Conclusion about regulatory characteristics of pleiotropic variants
%
\begin{itemize}
\item Variant pleiotropy is correlated in regions
\item Enrichment of variants upstream (incl. 5'UTR) and downstream of genes (incl. 3'UTR)
\item Enrichment of transcription factor and CRM binding
\item Increased number of associated egenes and etissues
\end{itemize}

@@

\begin{itemize}
\item A web portail to share data
\item Causality of egenes on gwas (Looking for experts ;-) )
\end{itemize}

>>>>

\begin{itemize}
\item Disease clusters are coherent
\item Definition of disease classes
\end{itemize}

@@

@@

@@

Outcomes interesting for the GOLD population genotypes
%
\begin{itemize}
\item A large set of causal GWAS variants annotated with target genes and tissues
\item A list of pleiotropic variants and regions
\end{itemize}
%
\vfill
%
What are the gene regulatory properties underlying pleiotropy between complex traits?
%
\begin{itemize}
\item Variant pleiotropy is correlated in regions
\item Enrichment of variants upstream (incl. 5'UTR) and downstream of genes (incl. 3'UTR)
\item Enrichment of transcription factor and CRM binding
\item Increased number of associated egenes and etissues
\end{itemize}

@@

\begin{itemize}
\item A web portail to share data
\item Causality of eQTL genes on GWAS (Looking for experts ;-) )
\end{itemize}
